Preparación de datos

### 2022-08-02 production/prod_analysis-fix-t5.Rmd
submission

view(df_individual,
     file = here::here("output/tables/ds_individual.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/ds_individual.html"),
        file =here::here("output/tables/ds_individual.png")) # Remover archivo HTML
# print(df, method = "render")

@@

view(df_municipal,
     file = here::here("output/tables/ds_municipal.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/ds_municipal.html"),
        file =here::here("output/tables/ds_municipal.png")) # Remover archivo HTML
# print(df, method = "render")
```

@@

  # Declare ggplot2 features
  ggplot2::theme_set(ggplot2::theme(panel.background = ggplot2::element_rect(fill = "gray85",
                                                                             colour = "gray85"),
                                    # panel.border = ggplot2::element_blank(),
                                    axis.text.y = ggplot2::element_text(size = 13,
                                                                        hjust = 1),
                                    title = ggplot2::element_text(size = 18,
                                                                  face = "bold"),
                                    legend.text = ggplot2::element_text(size = 12),
                                    plot.caption = ggplot2::element_text(size = 10,
                                                                         face = "plain",
                                                                         hjust = 1
                                                                         )))
#

@@

# plot individuales-----------------------------------------------------------
colors<- c("#b3b3b3ff","#f1eef6ff","#bdc9e1ff","#74a9cfff","#0570b0ff")
p_ansied<-
  dplyr::select(df_study1,in_ansied) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Convivality"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE) + 
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Neither comfortable nor uncomfortable",      
      "Very uncomfortable",
      "Uncomfortable",
      "Comfortable",
      "Very comfortable"
    )
  )

@@

p_convi<-
  dplyr::select(df_study1,in_valfam,in_valami,in_amigcl) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      # title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom")+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Disagree Neither disagree nor agree",      
      "Strongly disagree",
      "Disagree",
      "Agree",
      "Strongly agree"
    )
  )

@@

p_identi<-
  dplyr::select(df_study1,in_amsimb,in_acpier,in_acadop,
                in_amsimb:in_amreal) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      # title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom")+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Disagree Neither disagree nor agree",      
      "Strongly disagree",
      "Disagree",
      "Agree",
      "Strongly agree"
    )
  )

# Plot individual: THREAT -----------------------------------------------
p_threat<-
    dplyr::select(df_study1,in_amreal) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Disagree Neither disagree nor agree",      
      "Strongly disagree",
      "Disagree",
      "Agree",
      "Strongly agree"
    )
  )

# create plot-------------------------------------------------------------------
if (!require("pacman")) install.packages("pacman")
pacman::p_load(cowplot)
s <- 0.35
m <- 0.6
l <- 0.7
#Final plot
likert1<-   
  cowplot::add_sub(
    cowplot::plot_grid(p_ansied,p_simpat,p_convi,p_simili,p_identi,p_threat, 
                       align = "hv",
                       axis = "a",
                       nrow = 6, #4 plots
                       ncol = 1, #1 column
                       rel_heights = c(s,s,m,s,l,s) #fig size within plot
    ),
    label = paste0("Source: Own elaboration based on ELSOC Survey",
                   " (n=",dim(na.omit(df_study1))[1],")"
    ),        # Caption: source and sample size
    size = 12,  # Caption font size
    hjust = -0.25# Caption align
  ) %>%
  cowplot::ggdraw()  
# likert1
ggplot2::ggsave(filename = "plot_likert2.png",
                plot = likert1,
                path = here::here("output/images"),
                device = "png",
                units = "cm",
                scale = 3.5,
                width = 10,height = 10)
pacman::p_load(cowplot)

#Final plot
likert1<-   
  cowplot::add_sub(
    cowplot::plot_grid(p_a,p_b,p_c,p_d, #plot 1,2,3 and legend (bottom)
                       align = "hv",
                       axis = "a",
                       nrow = 4, #4 plots
                       ncol = 1, #1 column
                       rel_heights = c(0.25,0.25,0.25,0.90) #fig size within plot
    ),
    label = paste0("Source: Own elaboration based on ELSOC Survey",
                   " (n=",dim(na.omit(df_study1))[1],")"
    ),        # Caption: source and sample size
    size = 12,  # Caption font size
    hjust = -0.25# Caption align
  ) %>%
  cowplot::ggdraw()  
likert1
ggplot2::ggsave(filename = "plot_likert.png",
                plot = likert1,
                path = here::here("output/images"),
                device = "png",
                units = "cm",
                scale = 3,
                width = 10,height = 8)
```

@@

png(file=here::here("output/images/plot_corr.png"),width=900, height=700)
corrplot::corrplot(cor_full,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  # title = "\n Full sample"
  )
dev.off()

>>>>

view(df_individual,
     file = here::here("output/tables/ds_individual.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/ds_individual.html"),
        file =here::here("output/tables/table2.jpg")) # Remover archivo HTML
# print(df, method = "render")

@@

view(df_municipal,
     file = here::here("output/tables/ds_municipal.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/ds_municipal.html"),
        file =here::here("output/tables/table3.jpg")) # Remover archivo HTML
# print(df, method = "render")
```

@@

  # Declare ggplot2 features
  ggplot2::theme_set(ggplot2::theme(panel.background = ggplot2::element_rect(fill = "gray85",
                                                                             colour = "gray85"),
                                    panel.border = ggplot2::element_blank(),
                                    axis.text.y = ggplot2::element_text(size = 13,
                                                                        hjust = 1),
                                    title = ggplot2::element_text(size = 18,
                                                                  face = "bold"),
                                    legend.text = ggplot2::element_text(size = 12),
                                    plot.caption = ggplot2::element_text(size = 10,
                                                                         face = "plain",
                                                                         hjust = 1
                                                                         )
                                    )
                     )
#

@@

# plot individuales-----------------------------------------------------------
colors<- c("#b3b3b3ff","#f1eef6ff","#bdc9e1ff","#74a9cfff","#0570b0ff")
p_ansied<-
  dplyr::select(df_study1,in_ansied) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Convivality"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE) + 
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Neither comfortable nor uncomfortable",      
      "Very uncomfortable",
      "Uncomfortable",
      "Comfortable",
      "Very comfortable"
    )
  ) +
  ggplot2::geom_label(label.padding = 1, label.r = 1,label.size = 0.1)

p_ansied[["layers"]]

@@

p_convi<-
  dplyr::select(df_study1,in_valfam,in_valami,in_amigcl) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      # title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom")+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Neither disagree nor agree",      
      "Strongly disagree",
      "Disagree",
      "Agree",
      "Strongly agree"
    )
  )

@@

p_identi<-
  dplyr::select(df_study1,in_amsimb,in_acpier,in_acadop,
                in_amsimb) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      # title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom")+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Neither disagree nor agree",      
      "Strongly disagree",
      "Disagree",
      "Agree",
      "Strongly agree"
    )
  )

# Plot individual: THREAT -----------------------------------------------
p_threat<-
    dplyr::select(df_study1,in_amreal) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Neither disagree nor agree",      
      "Strongly disagree",
      "Disagree",
      "Agree",
      "Strongly agree"
    )
  )

# create plot-------------------------------------------------------------------
if (!require("pacman")) install.packages("pacman")
pacman::p_load(cowplot)
s <- 0.35
m <- 0.6
l <- 0.7
#Final plot
title <- cowplot::ggdraw() + 
  cowplot::draw_label(
    "Figure 1: Frequencies for Conviviality, Identity and Threat items",
    fontface = 'bold',
    size = 15,
    x = 0,
    hjust = 0
  )

likert1<-   
  cowplot::add_sub(
    cowplot::plot_grid(title,p_ansied,p_simpat,p_convi,p_simili,p_identi,p_threat, 
                       align = "hv",
                       axis = "a",
                       nrow = 6, #4 plots
                       ncol = 1, #1 column   
                       rel_heights = c(0.1,s,s,m,s,m,s) #fig size within plot
    ),
    label = paste0("Source: Own elaboration based on ELSOC Survey",
                   " (n=",dim(na.omit(df_study1))[1],")"
    ),        # Caption: source and sample size
    size = 12,  # Caption font size
    hjust = -0.25# Caption align  
  ) %>%
  cowplot::ggdraw()  
# likert1
ggplot2::ggsave(filename = "figure1.jpg",
                plot = likert1,
                path = here::here("output/images"),
                device = "jpg",
                units = "cm",
                scale = 3.5,
                width = 10,height = 10)
pacman::p_load(cowplot)

#Final plot
likert1<-   
  cowplot::add_sub(
    cowplot::plot_grid(p_a,p_b,p_c,p_d, #plot 1,2,3 and legend (bottom)
                       align = "hv",
                       axis = "a",
                       nrow = 4, #4 plots
                       ncol = 1, #1 column
                       rel_heights = c(0.25,0.25,0.25,0.90) #fig size within plot
    ),
    label = paste0("Source: Own elaboration based on ELSOC Survey",
                   " (n=",dim(na.omit(df_study1))[1],")"
    ),        # Caption: source and sample size
    size = 12,  # Caption font size
    hjust = -0.25# Caption align
  ) %>%
  cowplot::ggdraw()  
likert1
ggplot2::ggsave(filename = "figure1.jpg",
                plot = likert1,
                path = here::here("output/images"),
                device = "jpg",
                units = "cm",
                scale = 3,
                width = 10,height = 8)
```

@@

png(file=here::here("output/images/figure2.jpg"),width=900, height=700)
corrplot::corrplot(cor_full,
  title = "\nFigure 2: Polychoric correlation matrix for Conviviality, Identity and Threat items",
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  # title = "\n Full sample"
  )
dev.off()

### 2022-08-02 production/prod_prep.Rmd
submission

# Education_______________________________________
elsoc_long_2016_2021$educ <- 
  car::recode(elsoc_long_2016_2021$m01,
              "c(1,2,3)=1;c(4,5)=2;c(6,7)=3;c(8,9,10)=4; c(-888,-999)=NA")
elsoc_long_2016_2021$educ <-
  factor(elsoc_long_2016_2021$educ,
         labels = c("Primary","High school","Vocational","Universitary"))

>>>>

# Education_______________________________________
elsoc_long_2016_2021$educ <- 
  car::recode(elsoc_long_2016_2021$m01,
              "c(1,2,3)=1;c(4,5)=2;c(6,7)=3;c(8,9,10)=4; c(-888,-999)=NA")
elsoc_long_2016_2021$educ <-
  factor(elsoc_long_2016_2021$educ,
         labels = c("Primary","High school","Technical","Universitary"))
